### 2019-07-11 2-Chapters/4-Chapter/CrownCom_17.git/IoT_slotted.tex
Trying to kill this last empty page...

\begin{proposition}\label{prop:41:Lagrangian}
\begin{leftbar}[propositionbar]  % XXX leftbar propositionbar, comment if needed
    The \emph{Lagrange multipliers} method \cite{BoydVanderberghe04} can be used to solve the constraint real-valued maximization problem introduced in equation \eqref{eq:41:prob}.
    %
    It gives a closed form expression for the (unique) optimal solution $D_k^*(\lambda)$, depending on the system parameters, and the unknown Lagrange multiplier $\lambda \in \mathbb{R}$.
    %
    \begin{equation}\label{eq:41:Dilambda}
        D_k^*(\lambda) = \left(\frac{1}{\log(1-p)}\left[ \mathcal{W}\left(\frac{\lambda \e}{(1-p)^{S_k-1}} \right)-1 \right]\right)^{+} .
    \end{equation}
\end{leftbar}  % XXX leftbar propositionbar, comment if needed
\end{proposition}
%
\begin{smallproof}
\begin{itemize}
    \item
    In a realistic scenario, we can assume that $D_k\leq \frac{-2}{\ln\left(1-p\right)} \approx \frac{2}{p},\quad \forall k\in[K]$. For such values for $D_k$, the objective function $f: (D_1, \dots, D_{K}) \mapsto \sum_{k=1}^{K} D_k (1 - p)^{S_k + D_k -1}$ is concave as the sum of concave functions
    \footnote{~It is worth noting that $f$ is neither concave nor quasi-concave on $[0,\infty)^{K}$ \cite{Luenberger68,Yaari77}.}.
    \item
    The Lagrange multipliers method can be applied to the optimization problem \eqref{eq:41:optPb}, with a concave objective function $f$, linear equality constraints \eqref{eq:41:eqCstr} and linear inequality constraints \eqref{eq:41:ineqCstr}. The strong duality condition is satisfied in this case \cite{BoydVanderberghe04}, so finding the saddle points will be enough to find the maximizers.
    % \item
    % \hfill{}$\square$
    \end{itemize}
    More details are given in Section~\ref{sec:4:proofLagrangian} in the Appendix of this Chapter.
\end{smallproof}

@@

\textbf{Using a bandit algorithm for IoT devices.}
%
The IoT application is challenging in that there are \emph{multiple} players (the dynamic devices) interacting with the \emph{same} arms (the channels), without any centralized communication (they do not even know the total number of dynamic devices).
%
% Considered alone, each dynamic device
We propose algorithms in which each dynamic device ignores all the other one and
implements a learning algorithm to play a bandit game.
%
In each time slot, if it has to communicate (which happens with probability $p$), then it chooses a channel and it receives a reward $1$ if the transmission is successful, $0$ otherwise.
Each device aims at maximizing the sum of the rewards collected during its communication instants, which shall indeed maximize the fraction of successful transmissions. Besides the modified time scale (rewards are no longer collected at every time step), this looks like a usual bandit problem.
However, it cannot be modeled as a stochastic MAB, as the rewards are (unfortunately) \emph{not} \iid: they not only depend on the (stationary, \iid) behavior of the static devices, but also on the behavior of other dynamic devices, that is not stationary (because of learning and random activation of each device).
%
Despite this, we show in the next subsection that running a stochastic bandit algorithm for each device based on its own rewards is surprisingly successful.

\textbf{Considered algorithms.}
%
% In our model, every dynamic device implements its own algorithm, \emph{independently}.
% For one dynamic device, the time $t$ is the total number of sent messages from the beginning, as rewards are only obtained after a transmission.
%
The two algorithms we consider are \UCB{} (``\textcolor{blue}{UCB}'' in the figures)
and Thompson sampling (TS) (``\textcolor{red}{Thompson-sampling}''),
and they are presented in Section~\ref{sec:2:famousMABalgorithms}.
% originally $\alpha$ was set to $2$ \cite{Auer02}, but empirically $\alpha = 1/2$ is known to work better (uniformly across problems), and $\alpha > 1/2$ is advised by the theory \cite{Bubeck12}.
%
The \UCB{} algorithm uses $\alpha = 1/2$ in our experiments.
The TS algorithm is known to be empirically efficient, and for these reasons it has been used successfully in various applications, including problems from Cognitive Radio \cite{Toldov16,Mitton16}, and also in previous work on decentralized IoT-like networks \cite{Darak16}.
% although being simple and easy to implement, is known to perform well for stochastic problems, for which it was proven to be asymptotically optimal \cite{AgrawalGoyal11,Kaufmann12Thompson}.

\textbf{\emph{Adversarial} bandit algorithms?}
%
Instead of using MAB algorithms assuming a stochastic hypothesis on the system, we could try to use MAB algorithms designed to tackle a more general problem, that makes no hypothesis on the interfering traffic.
The \emph{adversarial MAB} algorithms is a broader family, of which a well-known and efficient example is the $\mathrm{Exp}3$ algorithm \cite{Auer02,Bubeck12}.
Empirically, the $\mathrm{Exp}3$ algorithm turned out to perform significantly worse than both \UCB{} and TS in the same experiments,
therefore we did not report results here.
% % FIXME maybe we should... ?
% %(see Section \ref{sub:41:numericalResults}).
% However, contrarily to the two stochastic algorithms, the use of $\mathrm{Exp}3$ is correctly justified, even in the non-stationary model, as its performance guarantees are true in \emph{any} setting.
% But it is not so surprising that it performs worse, as the theoretical performance guarantees of adversarial MAB algorithms are an order of magnitude
% %\footnote{~We preferred not to talk about \emph{regret} in this study, but in a few words: it is a measure of how \emph{bad} the algorithm performed in terms of its accumulated rewards, in comparison to the best possible policy, and should be as small as possible. For stochastic algorithms, being ``efficient'' means having a regret bounded as $R_T = \mathcal{O}(\log T)$, but for adversarial algorithms, it means having $R_T = \mathcal{O}(\sqrt{K T})$.}
% worse than the one for stochastic ones.
% (in their respective case of application).
% Further research on this aspect could lead to interesting future works.

@@

\begin{figure}[!h]
    \centering
    \subfloat[][10\% of dynamic devices]{\includegraphics[width=0.52\textwidth]{10intelligent.eps}
    \label{fig:41:10intelligent}}
    %
    \subfloat[][30\% of dynamic devices]{\includegraphics[width=0.52\textwidth]{30intelligent.eps}
    \label{fig:41:30intelligent}}
    %
    \vspace*{-10pt}
    \subfloat[][50\% of dynamic devices]{\includegraphics[width=0.52\textwidth]{50intelligent.eps}
    \label{fig:41:50intelligent}}
    %
    \subfloat[][100\% of dynamic devices]{\includegraphics[width=0.52\textwidth]{100intelligent.eps}
    \label{fig:41:100intelligent}}
    \caption[Performance of two MAB algorithms, \UCB{} and Thompson Sampling in red, compared to extreme reference policies without learning or oracle knowledge, when the proportion of dynamic end-devices in the network increases, from $10\%$ to $100\%$.]{Performance of two MAB algorithms, \textcolor{blue}{\UCB{} in blue} and \textcolor{red}{Thompson Sampling in red}, compared to extreme reference policies without learning or \textcolor{gold}{oracle knowledge}, when the proportion of dynamic end-devices in the network increases, from $10\%$ to $100\%$.}
    \label{fig:41:from10to100}
    \vspace*{-10pt}
\end{figure}

@@

\newpage % XXX

>>>>

\begin{proposition}\label{prop:41:Lagrangian}
\begin{leftbar}[propositionbar]  % XXX leftbar propositionbar, comment if needed
    The \emph{Lagrange multipliers} method \cite{BoydVanderberghe04} can be used to solve the constraint real-valued maximization problem introduced in equation \eqref{eq:41:prob}.
    %
    It gives a closed form expression for the (unique) optimal solution $D_k^*(\lambda)$, depending on the system parameters, and the unknown Lagrange multiplier $\lambda \in \mathbb{R}$.
    %
    \begin{equation}\label{eq:41:Dilambda}
        D_k^*(\lambda) = \left(\frac{1}{\log(1-p)}\left[ \mathcal{W}\left(\frac{\lambda \e}{(1-p)^{S_k-1}} \right)-1 \right]\right)^{+} .
    \end{equation}
\end{leftbar}  % XXX leftbar propositionbar, comment if needed
\end{proposition}
%
\begin{smallproof}
\begin{itemize}
    \item
    In a realistic scenario, we can assume that $D_k\leq \frac{-2}{\ln\left(1-p\right)} \approx \frac{2}{p},\quad \forall k\in[K]$. For such values for $D_k$, the objective function $f: (D_1, \dots, D_{K}) \mapsto \sum_{k=1}^{K} D_k (1 - p)^{S_k + D_k -1}$ is concave as the sum of concave functions%
    \footnote{~It is worth noting that $f$ is neither concave nor quasi-concave on $[0,\infty)^{K}$ \cite{Luenberger68,Yaari77}.}.
    \item
    The Lagrange multipliers method can be applied to the optimization problem \eqref{eq:41:optPb}, with a concave objective function $f$, linear equality constraints \eqref{eq:41:eqCstr} and linear inequality constraints \eqref{eq:41:ineqCstr}. The strong duality condition is satisfied in this case \cite{BoydVanderberghe04}, so finding the saddle points will be enough to find the maximizers.
    % \item
    % \hfill{}$\square$
    \end{itemize}
    More details are given in Section~\ref{sec:4:proofLagrangian} in the Appendix of this Chapter.
\end{smallproof}

@@

\paragraph{Using a bandit algorithm for IoT devices.}
%
The IoT application is challenging in that there are \emph{multiple} players (the dynamic devices) interacting with the \emph{same} arms (the channels), without any centralized communication (they do not even know the total number of dynamic devices).
%
% Considered alone, each dynamic device
We propose algorithms in which each dynamic device ignores all the other one and
implements a learning algorithm to play a bandit game.
%
In each time slot, if it has to communicate (which happens with probability $p$), then it chooses a channel and it receives a reward $1$ if the transmission is successful, $0$ otherwise.
Each device aims at maximizing the sum of the rewards collected during its communication instants, which shall indeed maximize the fraction of successful transmissions. Besides the modified time scale (rewards are no longer collected at every time step), this looks like a usual bandit problem.
However, it cannot be modeled as a stochastic MAB, as the rewards are (unfortunately) \emph{not} \iid: they not only depend on the (stationary, \iid) behavior of the static devices, but also on the behavior of other dynamic devices, that is not stationary (because of learning and random activation of each device).
%
Despite this, we show in the next subsection that running a stochastic bandit algorithm for each device based on its own rewards is surprisingly successful.

\paragraph{Considered algorithms.}
%
% In our model, every dynamic device implements its own algorithm, \emph{independently}.
% For one dynamic device, the time $t$ is the total number of sent messages from the beginning, as rewards are only obtained after a transmission.
%
The two algorithms we consider are \UCB{} (``\textcolor{blue}{UCB}'' in the figures)
and Thompson sampling (TS) (``\textcolor{red}{Thompson-sampling}''),
and they are presented in Section~\ref{sec:2:famousMABalgorithms}.
% originally $\alpha$ was set to $2$ \cite{Auer02}, but empirically $\alpha = 1/2$ is known to work better (uniformly across problems), and $\alpha > 1/2$ is advised by the theory \cite{Bubeck12}.
%
The \UCB{} algorithm uses $\alpha = 1/2$ in our experiments.
The TS algorithm is known to be empirically efficient, and for these reasons it has been used successfully in various applications, including problems from Cognitive Radio \cite{Toldov16,Mitton16}, and also in previous work on decentralized IoT-like networks \cite{Darak16}.
% although being simple and easy to implement, is known to perform well for stochastic problems, for which it was proven to be asymptotically optimal \cite{AgrawalGoyal11,Kaufmann12Thompson}.

\paragraph{\emph{Adversarial} bandit algorithms?}
%
Instead of using MAB algorithms assuming a stochastic hypothesis on the system, we could try to use MAB algorithms designed to tackle a more general problem, that makes no hypothesis on the interfering traffic.
The \emph{adversarial MAB} algorithms is a broader family, of which a well-known and efficient example is the $\mathrm{Exp}3$ algorithm \cite{Auer02,Bubeck12}.
Empirically, the $\mathrm{Exp}3$ algorithm turned out to perform significantly worse than both \UCB{} and TS in the same experiments,
therefore we did not report results here.
% % FIXME maybe we should... ?
% %(see Section \ref{sub:41:numericalResults}).
% However, contrarily to the two stochastic algorithms, the use of $\mathrm{Exp}3$ is correctly justified, even in the non-stationary model, as its performance guarantees are true in \emph{any} setting.
% But it is not so surprising that it performs worse, as the theoretical performance guarantees of adversarial MAB algorithms are an order of magnitude
% %\footnote{~We preferred not to talk about \emph{regret} in this study, but in a few words: it is a measure of how \emph{bad} the algorithm performed in terms of its accumulated rewards, in comparison to the best possible policy, and should be as small as possible. For stochastic algorithms, being ``efficient'' means having a regret bounded as $R_T = \mathcal{O}(\log T)$, but for adversarial algorithms, it means having $R_T = \mathcal{O}(\sqrt{K T})$.}
% worse than the one for stochastic ones.
% (in their respective case of application).
% Further research on this aspect could lead to interesting future works.

@@

\begin{figure}[!h]
    \centering
    \subfloat[][10\% of dynamic devices]{\includegraphics[width=0.52\textwidth]{10intelligent.eps}
    \label{fig:41:10intelligent}}
    %
    \subfloat[][30\% of dynamic devices]{\includegraphics[width=0.52\textwidth]{30intelligent.eps}
    \label{fig:41:30intelligent}}
    %
    \vspace*{-10pt}
    \subfloat[][50\% of dynamic devices]{\includegraphics[width=0.52\textwidth]{50intelligent.eps}
    \label{fig:41:50intelligent}}
    %
    \subfloat[][100\% of dynamic devices]{\includegraphics[width=0.52\textwidth]{100intelligent.eps}
    \label{fig:41:100intelligent}}
    \caption[Performance of two MAB algorithms, \UCB{} and Thompson Sampling in red, compared to extreme reference policies without learning or oracle knowledge, when the proportion of dynamic end-devices in the network increases, from $10\%$ to $100\%$.]{Performance of two MAB algorithms, \textcolor{blue}{\UCB{} in blue} and \textcolor{red}{Thompson Sampling in red}, compared to extreme reference policies without learning or \textcolor{gold}{oracle knowledge}, when the proportion of dynamic end-devices in the network increases, from $10\%$ to $100\%$.}
    \label{fig:41:from10to100}
    % \vspace*{-10pt}
\end{figure}

@@

% \newpage % XXX
